---
title: "Mapping Needs"
author: "Alexandra Gonzalez"
date: "1/14/2018"
output: html_document
---


## Overview & Purpose 

The purpose of this document is to take a sample of species, create a threat table
and import to ArcGis. 
In ArcGis, the goal is to create a join by species name and map the threats listed in
the table. 
         


```{r libraries_functions, include=FALSE}

## Look on IUCN website. Find 10 amphibian species where spatial data is avaialble. 
## Use written code to create a threat table of these 10 amphibain species with the 
## id_num. Then, import to ArcGis and map. 


library("profvis") 
library("rredlist")
library(RSQLite)
library(sqldf)
library(dplyr)
require(ggplot2)
require(reshape2)
require(scales)
token <- "cf51b7524f618f5b23220e687b70c01d0d240cc82d179cf2c5b08b70fdfb83d4" 


sp_threats <- function(species_list){
  threat_code <- vector(length = length(species_list),
                        mode = "character")
  i <- 1 
  for (species in species_list){
    threats <- rl_threats(species, key = token)
    code <- threats$result$code
    threat_code[i] <- paste(code, collapse = " ")
    i <- i + 1   
  }
  final_results <- data.frame(species_list, threat_code)
  return(final_results)
} #df of species and threat codes 
threat_table <- function(species_list){
  R1.1 <- rep(c(0),  each = length(species_list)) 
  R1.2 <- rep(c(0),  each = length(species_list))
  R1.3 <- rep(c(0),  each = length(species_list))
  
  #Agriculture and Aquaculture 
  A2.1 <- rep(c(0),  each = length(species_list))
  A2.1.1 <- rep(c(0),  each = length(species_list))
  A2.1.2 <- rep(c(0),  each = length(species_list))
  A2.1.3 <- rep(c(0),  each = length(species_list))
  A2.1.4 <- rep(c(0),  each = length(species_list))
  
  A2.2 <- rep(c(0),  each = length(species_list))
  A2.2.1 <- rep(c(0),  each = length(species_list))
  A2.2.2 <- rep(c(0),  each = length(species_list))
  A2.2.3 <- rep(c(0),  each = length(species_list))
  
  A2.3 <- rep(c(0),  each = length(species_list))
  A2.3.1 <- rep(c(0),  each = length(species_list))
  A2.3.2 <- rep(c(0),  each = length(species_list))
  A2.3.3 <- rep(c(0),  each = length(species_list))
  A2.3.4 <- rep(c(0),  each = length(species_list))
  
  A2.4 <- rep(c(0),  each = length(species_list))
  A2.4.1 <- rep(c(0),  each = length(species_list))
  A2.4.2 <- rep(c(0),  each = length(species_list))
  A2.4.3 <- rep(c(0),  each = length(species_list))
  
  #Energy Productoin and mining 
  E3.1 <- rep(c(0),  each = length(species_list)) 
  E3.2 <- rep(c(0),  each = length(species_list))
  E3.3 <- rep(c(0),  each = length(species_list)) 
  
  #Transportation and service corridots 
  T4.1 <- rep(c(0),  each = length(species_list))
  T4.2 <- rep(c(0),  each = length(species_list))
  T4.3 <- rep(c(0),  each = length(species_list))
  T4.4 <- rep(c(0),  each = length(species_list))
  
  #Biological Resource use 
  B5.1 <- rep(c(0),  each = length(species_list))
  B5.1.1 <- rep(c(0),  each = length(species_list))
  B5.1.2 <- rep(c(0),  each = length(species_list))
  B5.1.3 <- rep(c(0),  each = length(species_list))
  B5.1.4 <- rep(c(0),  each = length(species_list))
  
  B5.2 <- rep(c(0),  each = length(species_list))
  B5.2.1 <- rep(c(0),  each = length(species_list))
  B5.2.2 <- rep(c(0),  each = length(species_list))
  B5.2.3 <- rep(c(0),  each = length(species_list))
  B5.2.4 <- rep(c(0),  each = length(species_list))
  
  B5.3 <- rep(c(0),  each = length(species_list))
  B5.3.1 <- rep(c(0),  each = length(species_list))
  B5.3.2 <- rep(c(0),  each = length(species_list))
  B5.3.3 <- rep(c(0),  each = length(species_list))
  B5.3.4 <- rep(c(0),  each = length(species_list))
  B5.3.5 <- rep(c(0),  each = length(species_list))
  
  B5.4 <- rep(c(0),  each = length(species_list))
  B5.4.1 <- rep(c(0),  each = length(species_list))
  B5.4.2 <- rep(c(0),  each = length(species_list))
  B5.4.3 <- rep(c(0),  each = length(species_list))
  B5.4.4 <- rep(c(0),  each = length(species_list))
  B5.4.5 <- rep(c(0),  each = length(species_list))
  B5.4.6 <- rep(c(0),  each = length(species_list))
  
  #Human intrustions and disturbance 
  H6.1 <- rep(c(0),  each = length(species_list))  
  H6.2 <- rep(c(0),  each = length(species_list))
  H6.3 <- rep(c(0),  each = length(species_list))
  
  #Natural system modifications 
  N7.1 <- rep(c(0),  each = length(species_list))
  N7.1.1 <- rep(c(0),  each = length(species_list))
  N7.1.2 <- rep(c(0),  each = length(species_list))
  N7.1.3 <- rep(c(0),  each = length(species_list))
  
  N7.2 <- rep(c(0),  each = length(species_list))
  N7.2.11 <- rep(c(0),  each = length(species_list))
  N7.2.10 <- rep(c(0),  each = length(species_list))
  N7.2.1 <- rep(c(0),  each = length(species_list))
  N7.2.2 <- rep(c(0),  each = length(species_list))
  N7.2.3 <- rep(c(0),  each = length(species_list))
  N7.2.4 <- rep(c(0),  each = length(species_list))
  N7.2.5 <- rep(c(0),  each = length(species_list))
  N7.2.6 <- rep(c(0),  each = length(species_list))
  N7.2.7 <- rep(c(0),  each = length(species_list))
  N7.2.8 <- rep(c(0),  each = length(species_list))
  N7.2.9 <- rep(c(0),  each = length(species_list))
  
  N7.3 <- rep(c(0),  each = length(species_list))
  
  #Invasive and other problematic species, genes and disease 
  I8.1 <- rep(c(0),  each = length(species_list))
  I8.1.1 <- rep(c(0),  each = length(species_list))
  I8.1.2 <- rep(c(0),  each = length(species_list))
  
  I8.2 <- rep(c(0),  each = length(species_list))
  I8.2.1 <- rep(c(0),  each = length(species_list))
  I8.2.2 <- rep(c(0),  each = length(species_list))
  
  I8.3 <- rep(c(0),  each = length(species_list))
  
  I8.4 <- rep(c(0),  each = length(species_list))
  I8.4.1 <- rep(c(0),  each = length(species_list))
  I8.4.2 <- rep(c(0),  each = length(species_list))
  
  I8.5 <- rep(c(0),  each = length(species_list))
  I8.5.1 <- rep(c(0),  each = length(species_list))
  I8.5.2 <- rep(c(0),  each = length(species_list))
  
  I8.6 <- rep(c(0),  each = length(species_list))
  
  #Pollution 
  P9.1 <- rep(c(0),  each = length(species_list))
  P9.1.1 <- rep(c(0),  each = length(species_list))
  P9.1.2 <- rep(c(0),  each = length(species_list))
  P9.1.3 <- rep(c(0),  each = length(species_list))
  
  P9.2 <- rep(c(0),  each = length(species_list))
  P9.2.1 <- rep(c(0),  each = length(species_list))
  P9.2.2 <- rep(c(0),  each = length(species_list))
  P9.2.3 <- rep(c(0),  each = length(species_list))
  
  P9.3 <- rep(c(0),  each = length(species_list))
  P9.3.1 <- rep(c(0),  each = length(species_list))
  P9.3.2 <- rep(c(0),  each = length(species_list))
  P9.3.3 <- rep(c(0),  each = length(species_list))
  P9.3.4 <- rep(c(0),  each = length(species_list))
  
  P9.4 <- rep(c(0),  each = length(species_list))
  
  P9.5 <- rep(c(0),  each = length(species_list))
  P9.5.1 <- rep(c(0),  each = length(species_list))
  P9.5.2 <- rep(c(0),  each = length(species_list))
  P9.5.3 <- rep(c(0),  each = length(species_list))
  P9.5.4 <- rep(c(0),  each = length(species_list))
  
  P9.6 <- rep(c(0),  each = length(species_list))
  P9.6.1 <- rep(c(0),  each = length(species_list))
  P9.6.2 <- rep(c(0),  each = length(species_list))
  P9.6.3 <- rep(c(0),  each = length(species_list))
  P9.6.4 <- rep(c(0),  each = length(species_list))
  
  #Geological Events 
  G10.1 <- rep(c(0),  each = length(species_list))
  G10.2 <- rep(c(0),  each = length(species_list))
  G10.3 <- rep(c(0),  each = length(species_list))
  
  #Climate Change and severe weather 
  C11.1 <- rep(c(0),  each = length(species_list))
  C11.2 <- rep(c(0),  each = length(species_list))
  C11.3 <- rep(c(0),  each = length(species_list))
  C11.4 <- rep(c(0),  each = length(species_list))
  C11.5 <- rep(c(0),  each = length(species_list))
  
  #Other options 
  O12.1 <- rep(c(0),  each = length(species_list))
  
  threat_df <- data.frame(species_list, R1.1, R1.2, R1.3, A2.1, A2.1.1, A2.1.2, A2.1.3, A2.1.4,
                          A2.2, A2.2.1, A2.2.2, A2.2.3, A2.3, A2.3.1, A2.3.2, A2.3.3, A2.3.4, 
                          A2.4, A2.4.1, A2.4.2, A2.4.3, E3.1, E3.2, E3.3, T4.1, T4.2, T4.3, T4.4, 
                          B5.1, B5.1.1, B5.1.2, B5.1.3, B5.1.4, B5.2, B5.2.1, B5.2.2, B5.2.3, B5.2.4, 
                          B5.3, B5.3.1, B5.3.2, B5.3.3, B5.3.4, B5.3.5, B5.4, B5.4.1, B5.4.2, B5.4.3,
                          B5.4.4, B5.4.5, B5.4.6,
                          H6.1, H6.2, H6.3, N7.1, N7.1.1,
                          N7.1.2, N7.1.3, N7.2, N7.2.1, N7.2.2, N7.2.3, N7.2.4, N7.2.5, N7.2.6, N7.2.7,
                          N7.2.8, N7.2.9, N7.2.10, N7.2.11, N7.3, I8.1, I8.1.1, I8.1.2, I8.2, I8.2.1, 
                          I8.2.2, I8.3, I8.4, I8.4.1, I8.4.2, I8.5, I8.5.1, I8.5.2, I8.6, P9.1,P9.1.1,
                          P9.1.2, P9.1.3, P9.2,P9.2.1, P9.2.2, P9.2.3, P9.3, P9.3.1, P9.3.2, P9.3.3, 
                          P9.3.4, P9.4,P9.5, P9.5.1,P9.5.2, P9.5.3, P9.5.4, P9.6,P9.6.1, P9.6.2, P9.6.3, 
                          P9.6.4, G10.1, G10.2, G10.3, C11.1, C11.2, C11.3, C11.4, C11.5)
  return(threat_df)
} #Empty table of threats
pop_threat_tables <- function(data){
  ### data is a dataframe with the species_list  
  ### as one column and the threat_code as the
  ### other aims to work directly with sp_habitats 
  ###and habitat_tables 
  threatdf <- threat_table(data$species_list)
  i <- 1
  for (strings in data$threat_code){
    many_strings <- strsplit(strings, split = " ")
    for (elem in many_strings){
      for(code in elem){
        #### Residential 
        if (code == "1.1"){
          threatdf$R1.1[i] <- 1
        } else if (code == "1.2"){
          threatdf$R1.2[i] <- 1
        } else if (code == "1.3"){
          threatdf$R1.3[i] <- 1
          #### Agriculture 
        } else if (code == "2.1"){
          threatdf$A2.1[i] <- 1
        } else if (code == "2.1.1"){
          threatdf$A2.1.1[i] <- 1
        } else if (code == "2.1.2"){
          threatdf$A2.1.2[i] <- 1
        } else if (code == "2.1.3"){
          threatdf$A2.1.3[i] <- 1
        } else if (code == "2.1.4"){
          threatdf$A2.1.4[i] <- 1
          
        } else if (code == "2.2"){
          threatdf$A2.2[i] <- 1
        } else if (code == "2.2.1"){
          threatdf$A2.2.1[i] <- 1
        } else if (code == "2.2.2"){
          threatdf$A2.2.2[i] <- 1
        } else if (code == "2.2.3"){
          threatdf$A2.2.3[i] <- 1
          
        } else if (code == "2.3"){
          threatdf$A2.3[i] <- 1
        } else if (code == "2.3.1"){
          threatdf$A2.3.1[i] <- 1
        } else if (code == "2.3.2"){
          threatdf$A2.3.2[i] <- 1
        } else if (code == "2.3.3"){
          threatdf$A2.3.3[i] <- 1
        } else if (code == "2.3.4"){
          threatdf$A2.3.4[i] <- 1
          
        } else if (code == "2.4"){
          threatdf$A2.4[i] <- 1
        } else if (code == "2.4.1"){
          threatdf$A2.4.1[i] <- 1
        } else if (code == "2.4.2"){
          threatdf$A2.4.2[i] <- 1
        } else if (code == "2.4.3"){
          threatdf$A2.4.3[i] <- 1
          #### Energy 
        } else if (code == "3.1"){
          threatdf$E3.1[i] <- 1
        } else if (code == "3.2"){
          threatdf$E3.2[i] <- 1
        } else if (code == "3.3"){
          threatdf$E3.3[i] <- 1
          
          #### Transportation and service corridors 
        } else if (code == "4.1"){
          threatdf$T4.1[i] <- 1
        } else if (code == "4.2"){
          threatdf$T4.2[i] <- 1
        } else if (code == "4.3"){
          threatdf$T4.3[i] <- 1
        } else if (code == "4.4"){
          threatdf$T4.4[i] <- 1
          #### Biological resource use 
        } else if (code == "5.1"){
          threatdf$B5.1[i] <- 1
        } else if (code == "5.1.1"){
          threatdf$B5.1.1[i] <- 1
        } else if (code == "5.1.2"){
          threatdf$B5.1.2[i] <- 1
        } else if (code == "5.1.3"){
          threatdf$B5.1.3[i] <- 1
        } else if (code == "5.1.4"){
          threatdf$B5.1.4[i] <- 1
          
        } else if (code == "5.2"){
          threatdf$B5.2[i] <- 1
        } else if (code == "5.2.1"){
          threatdf$B5.2.1[i] <- 1
        } else if (code == "5.2.2"){
          threatdf$B5.2.2[i] <- 1
        } else if (code == "5.2.3"){
          threatdf$B5.2.3[i] <- 1
        } else if (code == "5.2.4"){
          threatdf$B5.2.4[i] <- 1
          
        } else if (code == "5.3"){
          threatdf$B5.3[i] <- 1
        } else if (code == "5.3.1"){
          threatdf$B5.3.1[i] <- 1
        } else if (code == "5.3.2"){
          threatdf$B5.3.2[i] <- 1
        } else if (code == "5.3.3"){
          threatdf$B5.3.3[i] <- 1
        } else if (code == "5.3.4"){
          threatdf$B5.3.4[i] <- 1
        } else if (code == "5.3.5"){
          threatdf$B5.3.5[i] <- 1
          
        } else if (code == "5.4"){
          threatdf$B5.4[i] <- 1
        } else if (code == "5.4.1"){
          threatdf$B5.4.1[i] <- 1
        } else if (code == "5.4.2"){
          threatdf$B5.4.2[i] <- 1
        } else if (code == "5.4.3"){
          threatdf$B5.4.3[i] <- 1
        } else if (code == "5.4.4"){
          threatdf$B5.4.4[i] <- 1
        } else if (code == "5.4.5"){
          threatdf$B5.4.5[i] <- 1
        } else if (code == "5.4.6"){
          threatdf$B5.4.6[i] <- 1
          
          #### Human intrustions 
        } else if (code == "6.1"){
          threatdf$H6.1[i] <- 1
        } else if (code == "6.2"){
          threatdf$H6.2[i] <- 1
        } else if (code == "6.3"){
          threatdf$H6.3[i] <- 1
          
          #### Natural system modifications 
        } else if (code == "7.1"){
          threatdf$N7.1[i] <- 1
        } else if (code == "7.1.1"){
          threatdf$N7.1.1[i] <- 1
        } else if (code == "7.1.2"){
          threatdf$N7.1.2[i] <- 1
        } else if (code == "7.1.3"){
          threatdf$N7.1.3[i] <- 1
          
        } else if (code == "7.2"){
          threatdf$N7.2[i] <- 1
        } else if (code == "7.2.1"){
          threatdf$N7.2.1[i] <- 1
        } else if (code == "7.2.2"){
          threatdf$N7.2.2[i] <- 1
        } else if (code == "7.2.3"){
          threatdf$N7.2.3[i] <- 1
        } else if (code == "7.2.4"){
          threatdf$N7.2.4[i] <- 1
        } else if (code == "7.2.5"){
          threatdf$N7.2.5[i] <- 1
        } else if (code == "7.2.6"){
          threatdf$N7.2.6[i] <- 1
        } else if (code == "7.2.7"){
          threatdf$N7.2.7[i] <- 1
        } else if (code == "7.2.8"){
          threatdf$N7.2.8[i] <- 1
        } else if (code == "7.2.9"){
          threatdf$N7.2.9[i] <- 1
        } else if (code == "7.2.10"){
          threatdf$N7.2.10[i] <- 1
        } else if (code == "7.2.11"){
          threatdf$N7.2.11[i] <- 1
          
        } else if (code == "7.3"){
          threatdf$N7.3[i] <- 1
          
          #### Invasive species/disease/introduced genes 
        } else if (code == "8.1"){
          threatdf$I8.1[i] <- 1
        } else if (code == "8.1.1"){
          threatdf$I8.1.1[i] <- 1
        } else if (code == "8.1.2"){
          threatdf$I8.1.2[i] <- 1
          
        } else if (code == "8.2"){
          threatdf$I8.2[i] <- 1
        } else if (code == "8.2.1"){
          threatdf$I8.2.1[i] <- 1
        } else if (code == "8.2.2"){
          threatdf$I8.2.2[i] <- 1
          
          
        } else if (code == "8.3"){
          threatdf$I8.3[i] <- 1
          
        } else if (code == "8.4"){
          threatdf$I8.4[i] <- 1
        } else if (code == "8.4.1"){
          threatdf$I8.4.1[i] <- 1
        } else if (code == "8.4.2"){
          threatdf$I8.4.2[i] <- 1
          
        } else if (code == "8.5"){
          threatdf$I8.5[i] <- 1
        } else if (code == "8.5.1"){
          threatdf$I8.5.1[i] <- 1
        } else if (code == "8.5.2"){
          threatdf$I8.5.2[i] <- 1
          
        } else if (code == "8.6"){
          threatdf$I8.6[i] <- 1
          
          #### Pollution
        } else if (code == "9.1"){
          threatdf$P9.1[i] <- 1
        } else if (code == "9.1.1"){
          threatdf$P9.1.1[i] <- 1
        } else if (code == "9.1.2"){
          threatdf$P9.1.2[i] <- 1
        } else if (code == "9.1.3"){
          threatdf$P9.1.3[i] <- 1
          
          
        } else if (code == "9.2"){
          threatdf$P9.2[i] <- 1
        } else if (code == "9.2.1"){
          threatdf$P9.2.1[i] <- 1
        } else if (code == "9.2.2"){
          threatdf$P9.2.2[i] <- 1
        } else if (code == "9.2.3"){
          threatdf$P9.2.3[i] <- 1
          
        } else if (code == "9.3"){
          threatdf$P9.3[i] <- 1
        } else if (code == "9.3.1"){
          threatdf$P9.3.1[i] <- 1
        } else if (code == "9.3.2"){
          threatdf$P9.3.2[i] <- 1
        } else if (code == "9.3.3"){
          threatdf$P9.3.3[i] <- 1
        } else if (code == "9.3.4"){
          threatdf$P9.3.4[i] <- 1
          
        } else if (code == "9.4"){
          threatdf$P9.4[i] <- 1
          
        } else if (code == "9.5"){
          threatdf$P9.5[i] <- 1
        } else if (code == "9.5.1"){
          threatdf$P9.5.1[i] <- 1
        } else if (code == "9.5.2"){
          threatdf$P9.5.2[i] <- 1
        } else if (code == "9.5.3"){
          threatdf$P9.5.3[i] <- 1
        } else if (code == "9.5.4"){
          threatdf$P9.5.4[i] <- 1
          
        } else if (code == "9.6"){
          threatdf$P9.6[i] <- 1
        } else if (code == "9.6.1"){
          threatdf$P9.6.1[i] <- 1
        } else if (code == "9.6.2"){
          threatdf$P9.6.2[i] <- 1
        } else if (code == "9.6.3"){
          threatdf$P9.6.3[i] <- 1
        } else if (code == "9.6.4"){
          threatdf$P9.6.4[i] <- 1
          
          #### Geological Events
        } else if (code == "10.1"){
          threatdf$G10.1[i] <- 1
        } else if (code == "10.2"){
          threatdf$G10.2[i] <- 1
        } else if (code == "10.3"){
          threatdf$G10.3[i] <- 1
          
          #### Climate Change
        } else if (code == "11.1"){
          threatdf$C11.1[i] <- 1
        } else if (code == "11.2"){
          threatdf$C11.2[i] <- 1
        } else if (code == "11.3"){
          threatdf$C11.3[i] <- 1
        } else if (code == "11.4"){
          threatdf$C11.4[i] <- 1
        } else if (code == "11.5"){
          threatdf$C11.5[i] <- 1
        }
      }
    }
    i <- 1 + i 
  }
  return(threatdf)
} #takes DF from sp_threats and populates empty threat table
```

#Sample sp that will be tested: 

#Amolops jinjiangensis (58212)
#Rhinella justinianoi (54675)
#Batrachuperus yenyuanensis (59088) 
#Barbourula busuangensis (23900)
#Eleutherodactylus cooki (7149) 
#Hypnobius arisanensis (59090)




```{r sample_sp, echo=TRUE}


#Choose a sample of species where spatial data is available 
#Create a small pop table, want to export to ArcGis and 
#see if I can create a join  
sample_species <- c("Amolops jinjiangensis","Rhinella justinianoi", "Batrachuperus yenyuanensis","Barbourula busuangensis", "Eleutherodactylus cooki")
practice <- sp_threats(sample_species)
practice
export_data <- pop_threat_tables(practice) 
write.csv (export_data, file = "sample_species3.csv")


```

# Sample Species update 
- Succesfully able to create the join on ArcGis 
- Data saved under Sample_Species on thumb drive 
- Figure out if ArcGis will be used or other r pacakge 
  make sure conservation mapping tool from Microsoft is gucci (that it doesn't conflict with what im doing)  i dont think it does - that was developed in 2014 and seems like it was made so that researches could input conservation data (including threats). This is then captured in the species range - doesnt seem like a widescale assesment has been completed of species threats 






## Next (Week of Jan. 16, 2017)

After the sample table has been imported and joined to ArcGis - here is a list of things that need to be taken care of next: 

1. Clean code (add descriptions - it is unclear what some of the functions mean)
  w/in herpetology folder - Code>Final Project.R has a list of all functions and analysis
2. Add id_num. Species name may not be enough when performing the join - need to capture
  the id as it is represented in IUCN database. 
3. Map all threats 
4. need to parse the threats by region 
  interesting - it seems as tho there are certain threats associated with 
  certain regions. therefore, plotting all of threats as is will be a problem
  
  
  
  
  maybe i can divide every species by region - and then plot by region 
  so species --> function that pulls out regions (ex. europe) --> pull out 
  species threats only in europe and map those 
  
  then you can map all species by a certain region at the same time 
  
  i think this makes sense 
  there are only 12 regions 
  might have to write more code - its not immediately obvious what the region of each   thing is  





  OKAY basically need to download all of the data again 
  because there was an update in the data (late 2017) - no point in doing the 
  maps with outdated data 